---
title: "Untitled"
format: html
---

join : to merge data set
```{r}
#| message: false
here::i_am("dplyr-102.Rproj")
library(here)
library(vroom) ## or readr
library(dplyr)
library(tidyr)
library(ggplot2)
```
## Data loading

```{r}
#| message: false
clients <- vroom(here("data","client.csv"))
account <- vroom(here("data","account.csv"))
disp <- vroom(here("data","disp.csv"))
```

## Joining data tables

A collection of joining functions of the form `*_join`

### Inner join

```{r}
da <- inner_join(account, disp)
```
here because there is only one common column, the function merges by default by that common column
the result is a cartesian product

```{r}
cda <- inner_join(clients, da, by=join_by("client_id"), suffix=c("_home", "_bank"))
```

### Home district versus bank district

```{r}
home_diff_bank <- cda |> filter(district_id_home!= district_id_bank) |> nrow()
```

We observe that `r homediff_bank` clients have a bank in another district as the one they live in.

```{r}
cda |> group_by(account_id)|> distinct(district_id_home) |> summarise(N=n()) |> filter(N>1)
```

### Gender gap ?

```{r}
clients |> count(gender)
```
```{r}
clients |> ggplot(aes(y=gender)) + geom_bar() + coord_flip()
```
```{r}
cda |> count(gender, type)
```
```{r}
cda |> count(gender, type) |> group_by(gender) |> mutate(freq= n/sum(n)) |> select(-n) |> ungroup() |> pivot_wider(values_from=freq, names_from=type)
```
```{r}
cda |> ggplot(aes(y=gender, fill=type)) + geom_bar(position="fill")
```

